Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-06-04 source/sec_intro.tex
Update sec_intro.tex

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|}\hline 
	Participation \textbackslash\ Objective function            & Strongly Convex        & Convex \\ \hline \hline
	Full                         & $\cO(\frac{1}{NT}+\frac{E^{2}}{T^{2}})$    &  $\mathcal{O}\left(\frac{1}{\sqrt{NT}}+\frac{NE^{2}}{T}\right)$       \\ \hline
	Partial                      &  $\cO\left(\frac{E^{2}}{KT}+\frac{E^{2}}{T^{2}}\right)$   &  $\cO\left(\frac{E^2}{\sqrt{KT}}+\frac{KE^2}{T} \right)$      \\ \hline
\end{tabular}
\caption{Our convergence results for FedAvg and Nesterov accelerated FedAvg in this paper.}
\label{tb:convergencerateintro}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|}\hline 
	Participation \textbackslash\ Objective function            & Strongly Convex        & Convex  & Overparameterized \\ \hline \hline
	Full                         & $\cO(\frac{1}{NT}+\frac{E^{2}}{T^{2}})$    &  $\mathcal{O}\left(\frac{1}{\sqrt{NT}}+\frac{NE^{2}}{T}\right)$   & $\cO(\exp(-\frac{NT}{E}))$    \\ \hline
	Partial                      &  $\cO\left(\frac{E^{2}}{KT}+\frac{E^{2}}{T^{2}}\right)$   &  $\cO\left(\frac{E^2}{\sqrt{KT}}+\frac{KE^2}{T} \right)$ & $\cO(\exp(-\frac{KT}{E}))$     \\ \hline
\end{tabular}
\caption{A high level summary of the convergence results for FedAvg and Nesterov accelerated FedAvg in this paper.}
\label{tb:convergencerateintro}
\end{table}

>>>>

\begin{table}[h!]
\centering
{\small
\begin{tabular}{|c|c|c|c|}\hline 
	Participation \textbackslash\ Objective function            & Strongly Convex        & Convex  & Overparameterized \\ \hline \hline
	Full                         & $\cO(\frac{1}{NT}+\frac{E^{2}}{T^{2}})$    &  $\mathcal{O}\left(\frac{1}{\sqrt{NT}}+\frac{NE^{2}}{T}\right)$   & $\cO(\exp(-\frac{NT}{E}))$    \\ \hline
	Partial                      &  $\cO\left(\frac{E^{2}}{KT}+\frac{E^{2}}{T^{2}}\right)$   &  $\cO\left(\frac{E^2}{\sqrt{KT}}+\frac{KE^2}{T} \right)$ & $\cO(\exp(-\frac{KT}{E}))$     \\ \hline
\end{tabular}
}
\caption{Our convergence results for FedAvg and Nesterov accelerated FedAvg in this paper.}
\label{tb:convergencerateintro}
\end{table}
